Sample size

### 2021-04-12 scripts/r/sample-size/sample-size.Rmd
:art: - update sample size figures (work in progress)

```{r plot}
tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds,
  min = sapply(sds, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

@@

tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_20,
  min = sapply(sds_20, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

@@

tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_40,
  min = sapply(sds_40, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

>>>>

```{r plot}
tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds,
  min = sapply(sds, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0)) +
  ylim(0, 8)

@@

tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_20,
  min = sapply(sds_20, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0)) +
  ylim(0, 8)

@@

tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_40,
  min = sapply(sds_40, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0)) +
  ylim(0, 8)
